Appendix of Bauer et al. (2023) Dike experiment

### 2023-02-22 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

@@

Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010; ID, 3271; WGS84, lat/lon, 48.85476, 12.918911) @cdc2022temp, @cdc2022prec] <!--# Check brackets -->and stream gauge Pfelling [ID: 10078000, WGS84, lat/lon, 48.87975, 12.74716, @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.

@@

@@

>>>>

<!--# Replace "Dike experiment" in the title -->

@@

Three dry years (2018--2020) and three minor floods (2018, 2019, 2021) occurred during the study period. Annual temperature, precipitation and discharge of River Danube near the study sites (2017--2021), based on weather station Metten [mean, 1981--2010, ID: 3271, WGS84: lat/lon, 48.85476, 12.918911, @cdc2022temp; @cdc2022prec] and stream gauge Pfelling [ID: 10078000, WGS84: lat/lon, 48.87975, 12.74716, @lfu2021discharge]. HQ2 = Highest discharge with a probability of occurrence every second year. HSW = Highest water level for shipping.

@@

The community-weighted means (CWM) of the seed mixtures used for the field experiment: specific leaf area (SLA), seed mass and canopy height. The CWMs were weighted by seed weight in the seed mixture and indicate differences between the target types hay meadows and dry calcareous grasslands. The functional traits of specific leaf area (SLA), seed mass and canopy height (available traits of all species: 99.2%, 98.8%, 99.6%) were retrieved from the databases LEDA [@Kleyer.2008] and TRY [@Kattge.2020].

```{r fig.id = "traits", fig.asp = 0.3030, fig.width = 6.49, fig.cap = ""}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_a3_800dpi_16.5x5cm_traits.tiff")
  )
```

### Acknowledgment

This figure has been supported by the TRY initiative on plant traits (<http://www.try-db.org>). The TRY initiative and database is hosted, developed and maintained by J. Kattge and G. Boenisch (Max Planck Institute for Biogeochemistry, Jena, Germany). TRY is currently supported by Future Earth/bioDISCOVERY and the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig.

\clearpage

\newpage

@@

\clearpage

\newpage

# Appendix A5
